---
output: html_document

---
# Assignment 9 :
Practice data analysis using r markdown using grad school admissions (GradSchool_Admissions.csv)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Package loading:
```{r, echo=TRUE,message=FALSE, warning=FALSE}
library(tidyverse)
library(modelr)
library(easystats)
library(plotly)
library(kableExtra)
library(janitor)
library(patchwork)
library(GGally)
```
Read in the data:
```{r, echo=TRUE}
df <- read.csv("../../Data/GradSchool_Admissions.csv") %>% 
  clean_names()
glimpse(df)

```
Clean it up a bit:
Make admissions logical
Make rank factor, not numeric

```{r}
df <- 
  df %>% 
  mutate(admitted = case_when(admit=="1" ~ TRUE,
                          admit=="0" ~ FALSE))

df$rank=as.factor(df$rank)

```

I'm not going to exclude any particular variables, because it makes sense that GPA, GRE score and rank of institution all have the potential to affect admission.
```{r}
view <- 
df %>% 
  select(admitted,gre,gpa,rank) %>% 
    ggpairs()

ggpairs(df)

mod1 = glm(data=df,
           formula=admit~gre)

mod2 = glm(data=df,
           formula=admit~gre + gpa )

mod3 = glm(data=df,
           formula=admit~(gre + gpa) * rank)

mod4 = glm(data=df,
           formula=admit~(gre*gpa) + rank)

mod4 = glm(data=df,
           formula=admit~(gre*gpa) + rank)
```

